Excel Constraints

### 2016-03-08 Progress.tex
Reorganized folder
Described the new algorithm

% Indentation
\setlength\parindent{0pt}

@@

\begin{figure}
  \centering
    \includegraphics[width=1\linewidth]{../Demo.png}
  \caption{Demo example}
  \label{fig:demo}
\end{figure}

@@

\section{Constraint-view Algorithm}
\subsection{Input}
The input to the algorithm consists of a set of version spaces~$S$ describing a hierarchical set of vectors.

@@

\begin{itemize}
 	\item For every free variable~$x$ in~$c$, prune~$S$ to obtain candidate values~$S_x$ using the properties that have been calculated so far: repeat:
 	\item For every version space~$s$ in~$S_x$, choose~$s$ as a value for $x$ and proceed
 	\item Use~$\rho_2$ to return the 
 \end{itemize}

>>>>

% Indentation
\setlength\parindent{0pt}
\graphicspath{{Graphics/}}

@@

\begin{figure}
  \centering
    \includegraphics[width=1\linewidth]{Demo.png}
  \caption{Demo example}
  \label{fig:demo}
\end{figure}

@@

{\color{gray}
\section{Constraint-view Algorithm (see sec~\ref{sec:algorithm2.0} for newer version)}

\subsection{Input}
The input to the algorithm consists of a set of version spaces~$S$ describing a hierarchical set of vectors.

@@

\begin{itemize}
 	\item For every free variable~$x$ in~$c$, prune~$S$ to obtain candidate values~$S_x$ using the properties that have been calculated so far: repeat:
 	\item For every version space~$s$ in~$S_x$, choose~$s$ as a value for $x$ and proceed
 	\item Use~$\rho_2$ to return the 
 \end{itemize}
}

\section{Algorithm 2.0}
\label{sec:algorithm2.0}

\subsection{Concepts \& Issues}
In order to abstract from the details of an excel sheet or CSV file, we use the notation introduced previously and reason about vectors and groups (powersets of vectors).
Based on the bias of the algorithm the powerset maybe be restricted to, for example, continuous ranges.
\\\\
Currently, transformations and dependencies between constraints are not really included in the algorithm.
They would, however, be useful for expressivity and eliminating redundancy, respectively.

\subsection*{Step 1: Group detection}
$\textit{CSV / Excel} \rightarrow \textit{Set of groups}$\\\\
In this step the input CSV / Excel file is analyzed and partitioned into a set of groups.
Preliminarily this step will be performed manually but it should be automized eventually.

\subsection*{Step 2: Constraint detection}
$\textit{Set of groups} \rightarrow \textit{Set of constraints}$\\\\
In this step all constraints that satisfy the data and the bias are detected and returned.
The main bias that will have to be accounted for is whether to return all, all most specific or all most general constraints.

\subsubsection*{Step 2.1: Constraint selection}
This step repeatedly selects a constraint template.
Constraints are found for every template and the constraints that have been found already are used to prune the results for the current template.

\subsubsection*{Step 2.2: Group selection}
The group selection step repeatedly assigns groups to the different free variables present in the constraint template.
It uses properties of the groups and preconditions on the variables imposed by the constraint template to avoid impossible assignments.
This step is either implemented directly or as a CSP.

\subsubsection*{Step 2.3: Subset selection}
The last step within constraint detection finds assignments of subgroups to variables such that they satisfy the constraint template.
It uses properties and the actually data to perform this step efficiently.
This step is realised by translating the assignment problem to a constraint-specific CSP that includes the actual data.

\subsection*{Step 3: Heuristic filtering}
$\textit{Set of constraints} \rightarrow \textit{Set of relevant constraints}$\\\\
In this last step the set of constraints is filtered and optionally ranked in order such that only relevant constraints are returned.
So far we have identified three (increasingly difficult) steps to find a heuristic.
First, rule of thumb heuristics can be used to prune some unlikely constraints.
In a second step, dependencies in the data can be used to identify useful constraints.
Finally, we can also attempt to learn what constraints are used frequently and how from existing data.
